Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-06 doc/JFLA2022/paper.tex
minor changes
add an active link to monorepos article; small changes
minor changes in conclusion

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France \\
  \email{pierre.casteran@labri.fr}
\and
Univ. de Paris, F-75013 Paris, France
\and
KTH Royal Institute of Technology, Stockholm, Sweden
\and
MIT CSAIL, Cambridge, Massachusetts, USA
\and
Inria, Univ. de Paris, CNRS, IRIF, UMR 8243, F-75013 Paris, France
}

@@

\Hydras wants to be a bridge between scientific litterature (\emph{e.g.}~\cite{KP82, KS81, schutte} and proof assistant technology. For the mathematician, it may give a concrete view of the mathematical content, not only through full proofs, but also through significative computations: examples, functions associated with constructive proofs, etc. For the \coq user, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. It may be also used as a library, through opam packages.

It is also a medium sized library (more than 50K LOC), dependent on various tools and libraries of the \coq ecosystem. It may be also used to experiment new techniques of continuous maintenance of the code and its documentation.

@@

We plan to extend our libraries in two main directions.

The \gaia project~\cite{Gaia}, also maintained on \community, contains a development by José Grimm~\cite{grimm:hal-00911710}. This library is dedicated  to the implementation in \coq (SSreflect) of books from  Bourbaki's Elements of Mathematics. It contains data structures which are compatible with our ordinal notations. 
Our plan is to build a  bridge between  the combinatorial results of \Hydras and the set-theoretic content of \gaia, and make possible the transfer of theorems between both libraries.

Another direction would be to write in \coq a formal proof of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.

>>>>

\institute{
Univ. Bordeaux, CNRS, Bordeaux INP, LaBRI, UMR 5800, F-33400 Talence, France  %\\
 % \email{pierre.casteran@labri.fr}
\and
Univ. de Paris, F-75013 Paris, France
\and
KTH Royal Institute of Technology, Stockholm, Sweden
\and
MIT CSAIL, Cambridge, Massachusetts, USA
\and
Inria, Univ. de Paris, CNRS, IRIF, UMR 8243, F-75013 Paris, France
}

@@

\Hydras wants to be a bridge between scientific litterature (\emph{e.g.}~\cite{KP82, KS81, schutte} and proof assistant technology. For the mathematician, it may give a concrete view of the mathematical content, not only through full proofs, but also through significative computations: examples, functions associated with constructive proofs, etc. For the \coq user, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50K LOC), dependent on various tools and libraries of the \coq ecosystem. It may be also used to experiment new techniques of continuous maintenance of the code and its documentation.

@@

We plan to extend our libraries in two main directions.
The \gaia project~\cite{Gaia}, also maintained on \community, contains a development by José Grimm~\cite{grimm:hal-00911710},  dedicated  to the implementation in \coq (SSreflect) of books from  Bourbaki's Elements of Mathematics. It contains data structures which are compatible with our ordinal notations. 
Our plan is to build a  bridge between  the combinatorial results of \Hydras and the set-theoretic content of \gaia, and make possible the transfer of theorems between both libraries.
We aim also to write in \coq a formal proof of the original statement of Theorem~\ref{kp:thm2}, using O'Connor's formalization of Peano Arithmetic~\cite{Goedel}.
